Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

\begin{table}[ht*]
\centering
\begin{tabular}{ l|l }
Hashtag & Count  \\
\hline
ff &     460 \\
np &     172 \\
nowplaying &     144 \\
winning &     134 \\
fb &     105 \\
rt &      83 \\
mentionke &      61 \\
blackpeoplemovies &      57 \\
tigerblood &      56 \\
thataintwinning &      53 \\
fail &      53 \\
teamfollowback &      52 \\
iftwitterwashighschool &      51 \\
bieberfact &      51 \\
news &      46 \\
jobs &      45 \\
libya &      44 \\
followmejp &      44 \\
partiu &      41 \\
sougofollow &      39 \\
damnitstrue &      39 \\
tilltheworldends &      37 \\
soalcinta &      35 \\
nicovideo &      35 \\
quran &      33 
\end{tabular}
\begin{tabular}{ l|l }
Hashtag & Count  \\
\hline
nw &      32 \\
quote &      31 \\
shoutout &      30 \\
jfb &      30 \\
carnaval &      27 \\
tfb &      26 \\
followme &      26 \\
followfriday &      25 \\
follow &      24 \\
egypt &      23 \\
retweet &      22 \\
fact &      22 \\
win &      20 \\
tweetmyjobs &      20 \\
music &      20 \\
in &      20 \\
imagine &      20 \\
nowwatching &      19 \\
cumannanyaindonesia &      19 \\
twexit &      18 \\
lcv &      18 \\
fui &      18 \\
bot &      18 \\
nemuritsuzuketeshinu &      17 \\
fato &      17 \\
\end{tabular}
\caption{Popular hashtags sampled during a three-day period.}\label{tbl:hashtags}
\end{table}

>>>>

\begin{table}[ht*]
\centering
\begin{tabular}{ l|l|l|l|l|l|l|l|l }
Hashtag & Count & $N_{ext}$ & $E(aut)$ & $Var(aut)$ & $E(ts)$ & $Var(ts)$ & $E(ts_{ext}$ & $Var(ts_{ext})$\\
\hline
ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
np &     172 & 48 & 0,4737 & 0,0287 & 0,0655 & 0,0196 & 0,0717 & 0,0195\\
nowplaying & 144 & 17 & 0,4514 & 0,0251 & 0,0565 & 0,0198 & 0,0458 & 0,0212 \\
winning &     134 & 48 & 0,8236 & 0,2365 & 0,1101 & 0,0666 & 0,1816 & 0,0272 \\
fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & 0.0208 & 0.0204 \\
rt & 83 & 48 & 1,7980 & 3,7309 & 0,0979 & 0,0763 & 0,1487 & 0,0267 \\
mentionke & 61 & 48 & 7,5459 & 195,6829 & 0,1406 & 0,0921 & 0,2215 & 0,0408 \\
blackpeoplemovies & 57 & 90,6195 & 2007,5551 & 0,3327 & 0,0606 & 0,0349 & 0,0244\\
tigerblood & 56 & 48 & 3,4029 & 4,8740 & 0,1497 & 0,0692 & 0,2330 & 0,0278 \\
thataintwinning & 53 & 48 & 16,8075 & 236,8694 & 0,0768 & 0,0435 & 0,1668 & 0,0387 \\
fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
teamfollowback & 52 & 48 & 0,9269 & 0,4871 & 0,1912 & 0,0932 & 0,1813 & 0,0245 \\
iftwitterwashighschool & 51 & 48 & 114,8342 & 1771,4564 & 0,5113 & 0,0405 & 0,5144 & 0,0352 \\
bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765\\
news & 46 & 0 & 1,8696 & 0,1943 & 0,1024 & 0,0210 & 0,0000 & 0,0000  \\
jobs & 45 & 0 & 1,3866 & 0,4198 & 0,1006 & 0,0192 & 0,0000 & 0,0000 \\
libya & 44 & 1 & 16,0309 & 117,2024 & 0,2701 & 0,0427 & 0,0208 & 0,0204 \\
followmejp & 44 & 0	& 1,5398 & 0,1255 & 0,0688 & 0,0410 & 0,0000 & 0,0000\\
partiu & 41 & 48 & 7,5809 & 84,0531 & 0,6042 & 0,2391 & 0,5313 & 0,2438 \\
sougofollow & 39 & 0 & 2,1010 & 0,1820 & 0,0720 & 0,0427 & 0,0000 & 0,0000 \\
damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
tilltheworldends & 37 & 48 & 85,4526 & 1366,8588 & 0,5682 & 0,0709 & 0,5116 & 0,0324 \\
soalcinta & 35 & 48 & 8,4143 & 103,7817 & 0,3451 & 0,1987 & 0,3120 & 0,2014 \\
nicovideo & 35 & 0	51,0720 & 5521,3529 & 0,3604 & 0,1893 & 0,0000 & 0,0000 \\
quran & 33 & 48 & 45,8290 & 90,4157 & 0,4271 & 0,0501 & 0,4188 & 0,0387 \\
%\end{tabular}
%\begin{tabular}{ l|l|l|l|l|l|l|l|l }
%Hashtag & Count  \\
%\hline
nw & 32 & 48 & 2,6054 & 2,1094 & 0,0672 & 0,0231 & 0,0901 & 0,0418 \\
quote & 31 & 48 & 4,3007 & 0,5706 & 0,1074 & 0,0197 & 0,1012 & 0,0212 \\
shoutout & 30 & 48 & 2,6030 & 3,3256 & 0,2347 & 0,0987 & 0,2526 & 0,0488 \\
jfb & 30 & 48 & 23,9911 & 1453,3113 & 0,2483 & 0,1654 & 0,2158 & 0,1379 \\
carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
tfb & 26 & 48 & 2,5994 & 0,8777 & 0,2292 & 0,1766 & 0,1760 & 0,0319 \\
followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	0.0000 &	0.0000 \\
followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
retweet & 22 & 48	4,6991 & 13,4434 & 0,1570 & 0,1232 & 0,1353 & 0,0306 \\
fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
win & 20 & 0 & 4,2949 & 5,1856 & 0,0347 & 0,0221 & 0,0000 & 0,0000 \\
tweetmyjobs & 20 & 0 & 35,5697 & 1590,6997 & 0,3244 & 0,0621 & 0,0000 & 0,0000 \\
music & 20 & 1 & 4,4665 & 4,6392 & 0,0833 & 0,0196 & 0,0208 & 0,0204 \\
in & 20 & 3	8,2367 & 6,8944 & 0,0649 & 0,0236 & 0,0251 & 0,0206 \\
imagine & 20 & 48	& 8,3378 & 30,4317 & 0,2465 & 0,1759 & 0,1813 & 0,1375 \\
nowwatching & 19 & 48 & 7,9110 & 8,6833 & 0,0672 & 0,0214 & 0,1293 & 0,0211 \\
cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
twexit & 18 & 48 & 12,5672 & 255,8178 & 0,3125 & 0,2148 & 0,2417 & 0,1783 \\
lcv & 18 & 48 & 28,6309 & 477,9193 & 0,4236 & 0,2395 & 0,2813 & 0,1969 \\
fui & 18 & 48 & 11,5515 & 165,3850 & 0,4896 & 0,2447 & 0,4635 & 0,2448 \\
bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & 0.0208 & 0.0204  \\
nemuritsuzuketeshinu & 17 & 48 & 314,1120 & 25053,5657 & 1,0000 & 0,0000 & 1,0000 & 0,0000 \\
fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
\end{tabular}
\caption{Popular hashtags sampled during a three-day period.}\label{tbl:hashtags}
\end{table}
